Latentcor: An R Package for Latent Correlation Estimation

### 2021-06-03 paper/paper.Rmd
Typo.

# Data generation
simdata <- GenerateData(n=n, trueidx1 = trueidx1, trueidx2 = trueidx2,
                        maxcancor = maxcancor,
                        Sigma1 = Sigma1, Sigma2 = Sigma2,
                        copula1 = "exp", copula2 = "cube",
                        muZ = mu,
                        type1 = "binary", type2 = "continuous",
                        c1 = rep(1, p1), c2 =  NULL
)
X1 <- simdata$X1; X2 <- simdata$X2; Sigma12_tt <- simdata$Sigma12
# Estimate latent correlation matrix with original method
R1_tt_org <- estR(X1, "binary", method = "original")
R2_tt_org <- estR(X2, "continuous", method = "original")
R12_tt_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "original")$R12
# Estimate latent correlation matrix with original method
R1_tt_org <- estR(X1, "binary", method = "approx")
R2_tt_org <- estR(X2, "continuous", method = "approx")
R12_tt_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "approx")$R12
```

>>>>

# Data generation
simdata <- GenerateData(n=n, trueidx1 = trueidx1, trueidx2 = trueidx2,
                        maxcancor = maxcancor,
                        Sigma1 = Sigma1, Sigma2 = Sigma2,
                        copula1 = "exp", copula2 = "cube",
                        muZ = mu,
                        type1 = "binary", type2 = "continuous",
                        c1 = rep(1, p1), c2 =  NULL
)
X1 <- simdata$X1; X2 <- simdata$X2; Sigma12_tt <- simdata$Sigma12
# Estimate latent correlation matrix with original method
R1_b_org <- estR(X1, "binary", method = "original")
R2_c_org <- estR(X2, "continuous", method = "original")
R12_bc_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "original")$R12
# Estimate latent correlation matrix with original method
R1_b_approx <- estR(X1, "binary", method = "approx")
R2_c_approx <- estR(X2, "continuous", method = "approx")
R12_bc_approx <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "approx")$R12
```
